Keyphrase Extraction from User Generated Contents on Medical Domain

### 2017-05-23 samplebody-conf.tex
edit foot note and several things

In this paper, we only focus the task of keyphrase extraction on Indonesian medical questions in online forum ,such as alodokter, health detik, doktergratis, dokter.id, doktersehat, klikdokter \footnote{www.alodokter.com, health.detik.com, www.dokter.id, www.doktersehat.com, www.klikdokter.com}. We present new keyphrases extraction techniques to extract more important information about the patient intentions and needs, which expressed inside Indonesian medical questions. Furthermore, we also propose a new definition of keyphrases, which is based on our observation of health-related and user-generated document. Actually, our final goal is to develop medical question answering systems to assist physicians or people obtaining health information. The work presented in this paper is absolutely inline with our goal, since important keyphrases of a question document can be used to formulate a query for the passage retrieval subsystem \cite{gong2009improving}. The example of keyphrase extraction in medical document can be seen below:

>>>>

In this paper, we only focus the task of keyphrase extraction on Indonesian medical questions in online forum ,such as alodokter\footnote{www.alodokter.com}, health detik \footnote{health.detik.com}, dokter.id \footnote{www.dokter.id}, klikdokter \footnote{www.klikdokter.com}. We present new keyphrases extraction techniques to extract more important information about the patient intentions and needs, which expressed inside Indonesian medical questions. Furthermore, we also propose a new definition of keyphrases, which is based on our observation of health-related and user-generated document. Actually, our final goal is to develop medical question answering systems to assist physicians or people obtaining health information. The work presented in this paper is absolutely inline with our goal, since important keyphrases of a question document can be used to formulate a query for the passage retrieval subsystem \cite{gong2009improving}. The example of keyphrase extraction in medical document can be seen below:
